### 2025-09-22 basic-statistics.qmd
20250922 - add df to ANOVA formula

$$
\begin{aligned}
  MS_{\text{between}} &= \frac{SS_{\text{between}}}{k - 1} \\
  MS_{\text{within}} &= \frac{SS_{\text{within}}}{N - k}
\end{aligned}
$$ {#eq-meanSquares}

where $k$ is the number of groups and $N$ is the sample size.

>>>>

$$
\begin{aligned}
  MS_{\text{between}} &= \frac{SS_{\text{between}}}{df_{\text{between}}} &=& \frac{SS_{\text{between}}}{k - 1} \\
  MS_{\text{within}}  &= \frac{SS_{\text{within}}}{df_{\text{within}}}   &=& \frac{SS_{\text{within}}}{N - k}
\end{aligned}
$$ {#eq-meanSquares}

where $df_{\text{between}}$ is the between-groups degrees of freedom, $df_{\text{within}}$ is the within-groups degrees of freedom, $k$ is the number of groups, and $N$ is the sample size.
